A 38 Million Year Old Mini-Neptune in the Kepler Field

### 2021-10-02 paper/ms.tex
update ms

Matching our young star list against stars observed by Kepler revealed that
%two discoveries.  The first, to be discussed in an upcoming analysis
%by J.~Curtis et al{.}, is that Kepler observed the $\approx$350\,Myr
%open cluster Theia~520 (UBC~1).  At least six Kepler planets are known
%in the cluster from the Kepler-52 and Kepler-968 systems
%\citep{rowe_validation_2014,jontof-hutter_following_2021}.  The second
%discovery, and the focus of this work, is
Kepler observed a portion of the \cn\ (Stephenson-1;
Theia~73).
More specifically, a clustering analysis of the Gaia
data by \citet{kounkel_untangling_2019}
reported that Kepler~1627 (KIC 6184894; KOI 5245; TIC 120105470) is a
\cn\ member.  Given the
previous statistical validation of the close-in mini-Neptune Kepler
1627b
\citep{2012ApJS..199...24T,morton_false_2016,thompson_planetary_2018},
we begin by examining the properties of the cluster more
closely (Section~\ref{sec:cluster}).  We find that the $\delta$ Lyr
cluster is \clusterage\ old, and 
in 
Section~\ref{sec:stars} show
that \sn\ is both a binary and also a member of the cluster.
Focusing on the planet (Section~\ref{sec:planet}), we confirm that despite the
presence of the previously unreported M2.5V companion, hereafter
Kepler\,1627B, the planet orbits the G-dwarf primary, Kepler\,1627A.  Based on a correlation between the
planetary transit times and the local light curve slope, the orbit
may also be prograde.  We conclude by highlighting broader
implications for our ability to age-date a larger sample of planets
(Section~\ref{sec:conc}).

@@

Figure~\ref{fig:age} shows that the \cn\ and IC\,2602 overlap, and
therefore are approximately the same age.  In our exploration, we also
compared against $\mu$-Tau ($62\pm7$\,Myr; \citealt{gagne_mutau_2020})
and the Upper-Centaurus-Lupus (UCL) component of the Sco OB2
association ($\approx$$16$\,Myr; \citealt{pecaut_star_2016}).  The
pre-main-sequence M dwarfs of the \cn\ were intermediate between the
latter two clusters.  To turn this heuristic interpolation into an age
measurement, we used the empirical method developed by
\citet{gagne_mutau_2020}.  In brief, we fitted the pre-main-sequence
loci of a set of reference clusters, and the locus of the target \cn\
was then modeled as a piecewise linear combination of these reference
clusters.  For our reference clusters, we adopted members of UCL,
IC\,2602, and the Pleiades from \citet{damiani_stellar_2019} and
\cite{CantatGaudin2018a} respectively.  We removed binaries by
requiring $\texttt{RUWE}<1.3$, $\texttt{radial\_velocity\_error}$
below the 80$^{\rm th}$ percentile of each cluster's distribution, and
manually excluded stars that were obvious photometric binaries in the
CAMD.  We then passed a moving box average and standard deviation
across the CAMD in 0.10\,mag bins, fitted a univariate spline to the
binned values, and assembled a piecewise grid of hybrid isochrones
spanning the ages between UCL to the Pleiades using Equations~6 and~7
from \citet{gagne_mutau_2020}.

@@

The ages returned by this procedure depend on the ages assumed for
each reference cluster.  We adopted a 115\,Myr age for the Pleiades \citep{dahm_2015},
and a 16\,Myr age for UCL \citep{pecaut_star_2016}.  The age
of IC\,2602 however is the most important ingredient, since it
receives the most weight in the interpolation.  Plausible ages for
IC\,2602 span 30\,Myr to 46\,Myr, with slightly older ages being
preferred by the lithium-depletion-boundary (LDB) measurements 
\citep{dobbie_ic_2010,randich_gaiaeso_2018}
and
younger ages by the main-sequence turn-off
\citep{stauffer_rotational_1997,david_ages_2015,bossini_age_2019}.
If we were to adopt the 30\,Myr age for IC\,2602, then the \cn\ would
be $31^{+5}_{-4}$\,Myr old.  For the converse extreme of 46\,Myr, the
\cn\ would be $44^{+8}_{-7}$\,Myr old.  We adopt an intermediate
38\,Myr age for IC\,2602, which yields an age for the \cn\ of
\clusterage.\footnote{Our exploration of the PARSEC and MIST isochrone
models over a grid of ages, metallicities, and reddenings, yielded the
best agreement for this $\approx 38\,$Myr age as well, given ${\rm
[Fe/H] = +0.1}$ and $A_V=0.2$
\citep{bressan_parsec_2012,choi_mesa_2016};  this preferred CAMD
reddening is higher than the \citet{lallement_threedimensional_2018}
value by a factor of two.  } Follow-up studies of the LDB or
main-sequence turn-off in the \cn\ could help determine a more precise
and accurate age for the cluster, and are left for future work.

@@

The adopted stellar parameters are listed in
Table~\ref{tab:starparams}.  The stellar mass, radius, and effective
temperature are found by interpolating against a 38$\,$Myr MIST
isochrone \citep{choi_mesa_2016}.  
The statistical uncertainties are propagated from the absolute
magnitude (mostly originating from the the parallax uncertainty) and the color; the systematic
uncertainties are taken to be the difference between the PARSEC
\citep{bressan_parsec_2012} and MIST isochrones.  Reported
uncertainties are a quadrature sum of the statistical and systematic
components.
As a consistency check, 
we analyzed the aforementioned Keck/HIRES spectrum from
the night of 2021 March 26 using a combination of
\texttt{SpecMatch-Emp} for stellar properties, and
\texttt{SpecMatch-Synth} for $v\sin i$
\citep{yee_SM_2017}.
This procedure yielded
$T_{\rm eff}=5498\pm100\,{\rm K}$,
$\log g=4.6\pm0.1$, $[{\rm Fe/H}]=0.15\pm0.10$ 
from \texttt{SpecMatch-Emp}, and $v\sin i = 18.9\pm1.0$ from
\texttt{SpecMatch-Synth}.
These values are within the $1$-$\sigma$ uncertainties of our adopted values from
the isochrone interpolation.

@@

Figure~\ref{fig:kep1627binary} summarizes the results of the
high-resolution imaging.  The Gaia EDR3 parallax for the primary
implies a projected separation of $53 \pm 4$\,AU, assuming the
companion is bound.  Although the companion is unresolved in the Gaia
source catalog (there are no comoving, codistant candidate companions
brighter than $G < 20.5$ mag within $\rho < 120\arcsec$), its
existence was also suggested by the primary star's large renormalized unit weight error (RUWE),
relative to other members of the \cn.  Based on the apparent
separation, the binary orbital period is of order hundreds of years.
The large RUWE is therefore more likely to be caused by a PSF-mismatch
skewing the Gaia centroiding during successive scans, rather than true
astrometric motion.  Regardless, given the low geometric probability that a companion imaged at
$\rho \approx 0\farcs16$ is a chance line-of-sight companion, we
proceed under the assumption that the companion is bound, and that
Kepler\,1627 is a binary.  
Given the distance and age, the models of
\citet{baraffe_new_2015} imply a companion mass of $M_{\rm B} \approx
0.33 M_{\odot}$ and companion temperature of $T_{\rm eff,B} \approx
3450$ K.  The corresponding spectral type is roughly M2.5V
\citep{pecaut_mamajek_2013}.
% \footnote{\url{http://www.pas.rochester.edu/~emamajek/EEM_dwarf_UBVIJHK_colors_Teff.txt}, version \texttt{2021/03/02}.}
These models combined with the NIRC2 contrast limits similarly imply
physical limits on tertiary companions of $M_{\rm ter} < 50
M_{\rm Jup}$ at $\rho = 50$\,AU, $M_{\rm ter} < 20 M_{\rm Jup}$ at $\rho =
100$\,AU, and $M_{\rm ter} < 10 M_{\rm Jup}$ at $\rho = 330$\,AU.

@@

The transit fit however is not perfect: the lower panels of
Figure~\ref{fig:lc} show an asymmetric
residual in the data relative to the model: the measured flux is systematically
high during the first half of transit, and low in the second half.  The
semi-amplitude of this deviation is $\approx50\,{\rm ppm}$, which
represents a $\approx 3\%$ distortion of the transit depth
($\approx1700\,{\rm ppm}$).  
Note that
while this asymmetry is within the 2-$\sigma$ model
uncertainties, the model has a jitter term that grows to
account for otherwise unmodeled white noise in the flux.  The
significance of the asymmetry is therefore best assessed in comparison
against the intrinsic out-of-transit scatter in the data, not the model
uncertainties.

To determine whether the asymmetry is a systematic caused by our stellar variability model,
we explored an alternative
approach in which we isolated each transit window and locally fitted
out polynomial trends, and then binned all the observed transits; the
asymmetry was still present at a comparable amplitude.  
Appendix~\ref{app:asymmetry} includes a deeper analysis, and
finds that the asymmetry also seems to be robust to different methods of
data binning.  Plausible astrophysical explanations are given in
Section~\ref{sec:conc}.

@@

More immediately, the Kepler data may yet contain additional
information.  For instance, one possible explanation for the transit
asymmetry shown in Figure~\ref{fig:lc} is that of a dusty asymmetric
outflow.  
A second possibility is that the planetary orbit is slightly misaligned
from the stellar spin axis, and tends to
transit starspot groups at
favored stellar latitudes.
Other possibilities such as gravity darkening or TTVs causing
the asymmetry are disfavored
(see Appendix~\ref{app:asymmetry}).  Dusty outflows are theoretically
expected for young mini-Neptunes, and the amplitude of the observed
asymmetry is also roughly consistent with predictions
\citep{wang_dai_2019}.  Beyond the asymmetric transits,
Appendix~\ref{app:flare} highlights an additional abnormality in the Kepler
data, in the arrival time distribution of stellar flares.  We
encourage its exploration by investigators more versed in the topic
than ourselves.

@@

The authors are grateful to J{.}~Winn, J{.}~Spake, A{.}~Howard, and
T{.}~David for illuminating discussions and suggestions, and to
R{.}~Kerr for kindly providing us with the \citet{Kerr2021} membership
list prior to its publication.
The authors are also grateful to K{.}~Collins for helping resolve the
scheduling conflict that would have otherwise prevented the MuSCAT3
observations.
% is grateful to G.~Zhou, B{.}~Tofflemire, A{.}~McWilliam,
% E{.}~Newton, M{.}~Kounkel, A{.}~Kraus, L{.}~Hillenbrand, and
% K{.}~Hawkins for the discussions on young stars, rotation, and lithium
% that encouraged this analysis.
%
L.G.B{.} acknowledges support from a Charlotte Elizabeth Procter
Fellowship from Princeton University, as well as from the TESS GI
Program, programs G011103 and G022117, through NASA grants
80NSSC19K0386 and 80NSSC19K1728.
%
%
Keck/NIRC2 imaging was acquired by program 2015A/N301N2L
(PI: A.~Kraus). % and 2019A/N069 (PI: E.~Petigura).
%
In addition, this paper is based in part on observations made with the
MuSCAT3 instrument, developed by the Astrobiology Center and under
financial support by JSPS KAKENHI (JP18H05439) and JST PRESTO
(JPMJPR1775), at Faulkes Telescope North on Maui, HI, operated by the
Las Cumbres Observatory.
%
This work is partly supported by JSPS KAKENHI Grant Numbers 22000005,
JP15H02063, JP17H04574, JP18H05439, JP18H05442, JST PRESTO Grant
Number JPMJPR1775, the Astrobiology Center of National Institutes of
Natural Sciences (NINS) (Grant Number AB031010).
%
% ACKNOWLEDGE PFS / CAMPANAS.
%
This paper also includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.
%
We thank the TESS Architects (G.~Ricker, R.~Vanderspek, D.~Latham,
S.~Seager, J.~Jenkins) and the many TESS team members for their
efforts to make the mission a continued success.
%
%
%This study was based in part on observations at Cerro Tololo
%Inter-American Observatory at NSF's NOIRLab (NOIRLab Prop{.} ID
%2020A-0146; 2020B-0029 PI: Bouma), which is managed by the
%Association of Universities for Research in Astronomy (AURA) under a
%cooperative agreement with the National Science Foundation.
%
%
Finally, this research has made use of the Keck Observatory Archive (KOA),
which is operated by the W. M. Keck Observatory and the NASA Exoplanet
Science Institute (NExScI), under contract with the National
Aeronautics and Space Administration.  We also thank the Keck
Observatory staff for their support of HIRES and remote observing.  We
recognize the importance that the summit of Maunakea has within the
indigenous Hawaiian community, and are deeply grateful to have the
opportunity to conduct observations from this mountain.
%
% The Digitized Sky Survey was produced at the Space Telescope Science
% Institute under U.S. Government grant NAG W-2166.
% Figure~\ref{fig:scene} is based on photographic data obtained using
% the Oschin Schmidt Telescope on Palomar Mountain.
%

@@

This means that the \texttt{age} column can be null, for cases in
which the original authors did not report an age, or for which a reference
literature age was not readily available.  Nonetheless, since we do
generally prefer stars with known ages, we made a few additional
efforts to populate this column.  When available, the age provenance
is from the original analysis of the cluster.  In a few cases
however we adopted other ages when string-based cross-matching on the
cluster name was straightforward.  In particular, we used the ages
determined by \citet{CantatGaudin2020b} to assign ages to the clusters
from \citet{GaiaCollaboration2018}, \citet{CantatGaudin2018a},
\citet{CastroGinard2020}, and \citet{CantatGaudin2020a}.

@@

For any of the catalogs for which Gaia DR2 identifiers were not
immediately available, we either followed the spatial (plus
proper-motion) cross-matching procedures described in
\citet{bouma_cdipsI_2019}, or else we pulled the Gaia DR2 source
identifiers associated with the catalog from SIMBAD.  We consequently
opted to drop the $\texttt{ext\_catalog\_name}$ and $\texttt{dist}$
columns maintained in \citet{bouma_cdipsI_2019}, as these were only
populated for a small number of stars.
The technical manipulations for the merging, cleaning, and joining
were performed using $\texttt{pandas}$
\citep{mckinney-proc-scipy-2010}.  The eventual cross-match (using the
Gaia DR2 $\texttt{source\_id}$) against the Gaia DR2 archive was
performed asychronously on the Gaia archive
website.\footnote{\url{https://gea.esac.esa.int/archive/}}

@@

Within the theory presented by \citet{mazeh_time_2015}, unresolved
starspot crossings cause the correlation between TTVs and the local
light curve slope (Figure~\ref{fig:corr}).  In this model, we would
expect the light curves with the most negative local slopes
to have the largest positive TTVs, due to spot crossing events during the latter
half of transit.  The lower-right panel of Figure~\ref{fig:phasettv}
and upper-left panel of Figure~\ref{fig:phaseslope} agree with this
expectation.  However, we would also expect the sign of the effect to
reverse when considering the most positive local slopes, and the most
negative TTVs.  The upper-left panel of Figure~\ref{fig:phasettv} and
lower-right panel of Figure~\ref{fig:phaseslope} contradict this
expectation: the residual in both cases maintains the same
parity!  On the one hand, this shows us that the residual is not
strongly dependent on the local light curve slope, which mitigates the
possibility that it might be an artifact of our detrending methods.
On the other, it raises the question of whether
unresolved starspot crossings are indeed the root cause of the correlation shown in
Figure~\ref{fig:corr}.

@@

Figure~\ref{fig:ground} shows the results.  The
MuSCAT3 photometry shows the expected starspot trend, along with the
transit and what is likely a chromatic starspot crossing event at
${\rm JD} - 2459433 = 0.955$.  The radial velocities decrease by
$\approx$250\ms\ over the six hour window.  
This decrease in RV is heavily with a decrease in the S-indices
derived from the Ca HK lines.
One outlying RV point is apparent shortly before egress; it is
temporally coincident with an outlying value in the S-index time series.

>>>>

Matching our young star list against stars observed by Kepler revealed that
%two discoveries.  The first, to be discussed in an upcoming analysis
%by J.~Curtis et al{.}, is that Kepler observed the $\approx$350\,Myr
%open cluster Theia~520 (UBC~1).  At least six Kepler planets are known
%in the cluster from the Kepler-52 and Kepler-968 systems
%\citep{rowe_validation_2014,jontof-hutter_following_2021}.  The second
%discovery, and the focus of this work, is
Kepler observed a portion of the \cn\ (Stephenson-1;
Theia~73).
More specifically, a clustering analysis of the Gaia
data by \citet{kounkel_untangling_2019}
reported that Kepler~1627 (KIC 6184894; KOI 5245; TIC 120105470) is a
\cn\ member.  Given the
previous statistical validation of the close-in mini-Neptune Kepler
1627b
\citep{2012ApJS..199...24T,morton_false_2016,thompson_planetary_2018},
we begin by examining the properties of the cluster (Section~\ref{sec:cluster}).  We find that the $\delta$ Lyr
cluster is \clusterage\ old, and 
in 
Section~\ref{sec:stars} show
that \sn\ is both a binary and also a member of the cluster.
Focusing on the planet (Section~\ref{sec:planet}), we confirm that despite the
presence of the previously unreported M2.5V companion, hereafter
Kepler\,1627B, the planet orbits the G-dwarf primary, Kepler\,1627A.  Based on a correlation between the
planetary transit times and the local light curve slope, the orbit
may also be prograde.  We conclude by highlighting broader
implications for our ability to age-date a larger sample of planets
(Section~\ref{sec:conc}).

@@

Figure~\ref{fig:age} shows that the \cn\ and IC\,2602 overlap, and
therefore are approximately the same age.  In our exploration, we also
compared against $\mu$-Tau ($62\pm7$\,Myr; \citealt{gagne_mutau_2020})
and the Upper-Centaurus-Lupus (UCL) component of the Sco OB2
association ($\approx$$16$\,Myr; \citealt{pecaut_star_2016}).  The
pre-main-sequence M dwarfs of the \cn\ were intermediate between the
latter two clusters.  To turn this heuristic interpolation into an age
measurement, we used the empirical method developed by
\citet{gagne_mutau_2020}.  In brief, we fitted the pre-main-sequence
loci of a set of reference clusters, and the locus of the target \cn\
was then modeled as a piecewise linear combination of these reference
clusters.  For our reference clusters, we adopted members of UCL,
IC\,2602, and the Pleiades from \citet{damiani_stellar_2019} and
\cite{CantatGaudin2018a} respectively.  We removed binaries by
requiring $\texttt{RUWE}<1.3$, $\texttt{radial\_velocity\_error}$
below the 80$^{\rm th}$ percentile of each cluster's distribution, and
excluded stars that were obvious photometric binaries in the
CAMD.  We then passed a moving box average and standard deviation
across the CAMD in 0.10\,mag bins, fitted a univariate spline to the
binned values, and assembled a piecewise grid of hybrid isochrones
spanning the ages between UCL to the Pleiades using Equations~6 and~7
from \citet{gagne_mutau_2020}.

@@

The ages returned by this procedure depend on the ages assumed for
each reference cluster.  We adopted a 115\,Myr age for the Pleiades \citep{dahm_2015},
and a 16\,Myr age for UCL \citep{pecaut_star_2016}.  The age
of IC\,2602 however is the most important ingredient, since it
receives the most weight in the interpolation.  Plausible ages for
IC\,2602 span 30\,Myr to 46\,Myr, with older ages being
preferred by the lithium-depletion-boundary (LDB) measurements 
\citep{dobbie_ic_2010,randich_gaiaeso_2018}
and
younger ages by the main-sequence turn-off
\citep{stauffer_rotational_1997,david_ages_2015,bossini_age_2019}.
If we were to adopt the 30\,Myr age for IC\,2602, then the \cn\ would
be $31^{+5}_{-4}$\,Myr old.  For the converse extreme of 46\,Myr, the
\cn\ would be $44^{+8}_{-7}$\,Myr old.  We adopt an intermediate
38\,Myr age for IC\,2602, which yields an age for the \cn\ of
\clusterage.\footnote{Our exploration of the PARSEC and MIST isochrone
models over a grid of ages, metallicities, and reddenings, yielded the
best agreement for this $\approx 38\,$Myr age as well, given ${\rm
[Fe/H] = +0.1}$ and $A_V=0.2$
\citep{bressan_parsec_2012,choi_mesa_2016};  this preferred CAMD
reddening is higher than the \citet{lallement_threedimensional_2018}
value by a factor of two.  } Follow-up studies of the LDB or
main-sequence turn-off in the \cn\ could help determine a more precise
and accurate age for the cluster, and are left for future work.

@@

The adopted stellar parameters are listed in
Table~\ref{tab:starparams}.  The stellar mass, radius, and effective
temperature are found by interpolating against a 38$\,$Myr MIST
isochrone \citep{choi_mesa_2016}.  
The statistical uncertainties are propagated from the absolute
magnitude (mostly originating from the parallax uncertainty) and the color; the systematic
uncertainties are taken to be the difference between the PARSEC
\citep{bressan_parsec_2012} and MIST isochrones.  Reported
uncertainties are a quadrature sum of the statistical and systematic
components.
As a consistency check, 
we analyzed the aforementioned Keck/HIRES spectrum from
the night of 2021 March 26 using a combination of
\texttt{SpecMatch-Emp} for stellar properties, and
\texttt{SpecMatch-Synth} for $v\sin i$
\citep{yee_SM_2017}.
This procedure yielded
$T_{\rm eff}=5498\pm100\,{\rm K}$,
$\log g=4.6\pm0.1$, $[{\rm Fe/H}]=0.15\pm0.10$ 
from \texttt{SpecMatch-Emp}, and $v\sin i = 18.9\pm1.0$ from
\texttt{SpecMatch-Synth}.
These values are within the $1$-$\sigma$ uncertainties of our adopted values from
the isochrone interpolation.

@@

Figure~\ref{fig:kep1627binary} summarizes the results of the
high-resolution imaging.  The Gaia EDR3 parallax for the primary
implies a projected separation of $53 \pm 4$\,AU, assuming the
companion is bound.  Although the companion is unresolved in the Gaia
source catalog (there are no comoving, codistant candidate companions
brighter than $G < 20.5$ mag within $\rho < 120\arcsec$), its
existence was also suggested by the primary star's large renormalized unit weight error (RUWE),
relative to other members of the \cn.  Based on the apparent
separation, the binary orbital period is of order hundreds of years.
The large RUWE is therefore more likely to be caused by a PSF-mismatch
skewing the Gaia centroiding during successive scans, rather than true
astrometric motion.  Regardless, given the low geometric probability that a companion imaged at
$\rho \approx 0\farcs16$ is a chance line-of-sight companion, we
proceed under the assumption that the companion is bound, and that
Kepler\,1627 is a binary.  
Given the distance and age, the models of
\citet{baraffe_new_2015} imply a companion mass of $M_{\rm B} \approx
0.33 M_{\odot}$ and companion temperature of $T_{\rm eff,B} \approx
3450$ K.  The corresponding spectral type is roughly M2.5V
\citep{pecaut_mamajek_2013}.
% \footnote{\url{http://www.pas.rochester.edu/~emamajek/EEM_dwarf_UBVIJHK_colors_Teff.txt}, version \texttt{2021/03/02}.}
These models combined with the NIRC2 contrast limits imply
physical limits on tertiary companions of $M_{\rm ter} < 50
M_{\rm Jup}$ at $\rho = 50$\,AU, $M_{\rm ter} < 20 M_{\rm Jup}$ at $\rho =
100$\,AU, and $M_{\rm ter} < 10 M_{\rm Jup}$ at $\rho = 330$\,AU.

@@

The transit fit however is not perfect: the lower panels of
Figure~\ref{fig:lc} show an asymmetric
residual in the data relative to the model: the measured flux is 
high during the first half of transit, and low in the second half.  The
semi-amplitude of this deviation is $\approx50\,{\rm ppm}$, which
represents a $\approx 3\%$ distortion of the transit depth
($\approx1700\,{\rm ppm}$).  
Note that
while this asymmetry is within the 2-$\sigma$ model
uncertainties, the model has a jitter term that grows to
account for otherwise unmodeled white noise in the flux.  The
significance of the asymmetry is therefore best assessed in comparison
against the intrinsic out-of-transit scatter in the data, not the model
uncertainties.

To determine whether the asymmetry is a systematic caused by our stellar variability model,
we explored an alternative
approach in which we isolated each transit window and locally fitted
out polynomial trends, and then binned all the observed transits; the
asymmetry was still present at a comparable amplitude.  
Appendix~\ref{app:asymmetry} includes a deeper analysis, and
finds that the asymmetry also seems to be robust to different methods of
data binning.  The most likely astrophysical explanations are
discussed in
Section~\ref{sec:conc}.

@@

More immediately, the Kepler data may yet contain additional
information.  For instance, one possible explanation for the transit
asymmetry shown in Figure~\ref{fig:lc} is that of a dusty asymmetric
outflow.  
A second possibility is that the planetary orbit is slightly misaligned
from the stellar spin axis, and tends to
transit starspot groups at
favored stellar latitudes.
Other possibilities such as gravity darkening or TTVs causing
the asymmetry are disfavored
(see Appendix~\ref{app:asymmetry}).  Dusty outflows are theoretically
expected for young mini-Neptunes, and the amplitude of the observed
asymmetry is also consistent with predictions
\citep{wang_dai_2019}.  Beyond the asymmetric transits,
Appendix~\ref{app:flare} highlights an additional abnormality in the Kepler
data, in the arrival time distribution of stellar flares.  We
encourage its exploration by investigators more versed in the topic
than ourselves.

@@

The authors are grateful to J{.}~Winn, J{.}~Spake, A{.}~Howard, and
T{.}~David for illuminating discussions and suggestions, and to
R{.}~Kerr for providing us with the \citet{Kerr2021} membership
list prior to its publication.
The authors are also grateful to K{.}~Collins for helping resolve the
scheduling conflict that would have otherwise prevented the MuSCAT3
observations.
% is grateful to G.~Zhou, B{.}~Tofflemire, A{.}~McWilliam,
% E{.}~Newton, M{.}~Kounkel, A{.}~Kraus, L{.}~Hillenbrand, and
% K{.}~Hawkins for the discussions on young stars, rotation, and lithium
% that encouraged this analysis.
%
L.G.B{.} acknowledges support from a Charlotte Elizabeth Procter
Fellowship from Princeton University, as well as from the TESS GI
Program, programs G011103 and G022117, through NASA grants
80NSSC19K0386 and 80NSSC19K1728.
%
%
Keck/NIRC2 imaging was acquired by program 2015A/N301N2L
(PI: A.~Kraus). % and 2019A/N069 (PI: E.~Petigura).
%
In addition, this paper is based in part on observations made with the
MuSCAT3 instrument, developed by the Astrobiology Center and under
financial support by JSPS KAKENHI (JP18H05439) and JST PRESTO
(JPMJPR1775), at Faulkes Telescope North on Maui, HI, operated by the
Las Cumbres Observatory.
%
This work is partly supported by JSPS KAKENHI Grant Numbers 22000005,
JP15H02063, JP17H04574, JP18H05439, JP18H05442, JST PRESTO Grant
Number JPMJPR1775, the Astrobiology Center of National Institutes of
Natural Sciences (NINS) (Grant Number AB031010).
%
% ACKNOWLEDGE PFS / CAMPANAS.
%
This paper also includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.
%
We thank the TESS Architects (G.~Ricker, R.~Vanderspek, D.~Latham,
S.~Seager, J.~Jenkins) and the many TESS team members for their
efforts to make the mission a continued success.
%
%
%This study was based in part on observations at Cerro Tololo
%Inter-American Observatory at NSF's NOIRLab (NOIRLab Prop{.} ID
%2020A-0146; 2020B-0029 PI: Bouma), which is managed by the
%Association of Universities for Research in Astronomy (AURA) under a
%cooperative agreement with the National Science Foundation.
%
%
Finally, this research has made use of the Keck Observatory Archive (KOA),
which is operated by the W. M. Keck Observatory and the NASA Exoplanet
Science Institute (NExScI), under contract with the National
Aeronautics and Space Administration.  We also thank the Keck
Observatory staff for their support of HIRES and remote observing.  We
recognize the importance that the summit of Maunakea has within the
indigenous Hawaiian community, and are deeply grateful to have the
opportunity to conduct observations from this mountain.
%
% The Digitized Sky Survey was produced at the Space Telescope Science
% Institute under U.S. Government grant NAG W-2166.
% Figure~\ref{fig:scene} is based on photographic data obtained using
% the Oschin Schmidt Telescope on Palomar Mountain.
%

@@

This means that the \texttt{age} column can be null, for cases in
which the original authors did not report an age, or for which a reference
literature age was not readily available.  Nonetheless, since we do
prefer stars with known ages, we made a few additional
efforts to populate this column.  When available, the age provenance
is from the original analysis of the cluster.  In a few cases
however we adopted other ages when string-based cross-matching on the
cluster name was straightforward.  In particular, we used the ages
determined by \citet{CantatGaudin2020b} to assign ages to the clusters
from \citet{GaiaCollaboration2018}, \citet{CantatGaudin2018a},
\citet{CastroGinard2020}, and \citet{CantatGaudin2020a}.

@@

For any of the catalogs for which Gaia DR2 identifiers were not
available, we either followed the spatial (plus
proper-motion) cross-matching procedures described in
\citet{bouma_cdipsI_2019}, or else we pulled the Gaia DR2 source
identifiers associated with the catalog from SIMBAD.  We consequently
opted to drop the $\texttt{ext\_catalog\_name}$ and $\texttt{dist}$
columns maintained in \citet{bouma_cdipsI_2019}, as these were only
populated for a small number of stars.
The technical manipulations for the merging, cleaning, and joining
were performed using $\texttt{pandas}$
\citep{mckinney-proc-scipy-2010}.  The eventual cross-match (using the
Gaia DR2 $\texttt{source\_id}$) against the Gaia DR2 archive was
performed asychronously on the Gaia archive
website.\footnote{\url{https://gea.esac.esa.int/archive/}}

@@

Within the theory presented by \citet{mazeh_time_2015}, unresolved
starspot crossings cause the correlation between TTVs and the local
light curve slope (Figure~\ref{fig:corr}).  In this model, we would
expect the light curves with the most negative local slopes
to have the largest positive TTVs, due to spot crossing events during the latter
half of transit.  The lower-right panel of Figure~\ref{fig:phasettv}
and upper-left panel of Figure~\ref{fig:phaseslope} agree with this
expectation.  However, we would also expect the sign of the effect to
reverse when considering the most positive local slopes, and the most
negative TTVs.  The upper-left panel of Figure~\ref{fig:phasettv} and
lower-right panel of Figure~\ref{fig:phaseslope} contradict this
expectation: the residual in both cases maintains the same
parity!  On the one hand, this shows us that the residual is not
dependent on the local light curve slope, which mitigates the
possibility that it might be an artifact of our detrending methods.
On the other, it raises the question of whether
unresolved starspot crossings are indeed the root cause of the correlation shown in
Figure~\ref{fig:corr}.

@@

Figure~\ref{fig:ground} shows the results.  The
MuSCAT3 photometry shows the expected starspot trend, along with the
transit and what is likely a chromatic starspot crossing event at
${\rm JD} - 2459433 = 0.955$.  The radial velocities decrease by
$\approx$250\ms\ over the six hour window.  
This decrease in RV is correlated with a decrease in the S-indices
derived from the Ca HK lines.
One outlying RV point is apparent shortly before egress; it is
temporally coincident with an outlying value in the S-index time series.
